Applying a clever histogram method to the square-well liquid

### 2014-05-28 papers/square-well-liquid/histogram-paper.tex
decrease # of spheres yet again (and increase iterations) for "quick" SW MC plots Tested on bennet. Took 3:00.68.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N100-E}
  \caption{A histogram plot demonstrating the difficulty of using
    canonical Monte Carlo to simulate a system.  A simulation at a
    give temperature only provides information fo a small number of
    energy states.\label{fig:histograms}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N100-dos}
  \caption{A density of states plot demonstrating the difficulty of using
    canonical Monte Carlo to simulate a system.  A simulation at a
    give temperature only provides information fo a small number of
    energy states.\label{fig:dos}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N100-u}
  \caption{Specific internal energy.\label{fig:u}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N100-hc}
  \caption{Specific heat capacity.\label{fig:hc}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N100-rdf}
  \caption{Radial distribution function.\label{fig:rdf}}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-E}
  \caption{A histogram plot demonstrating the difficulty of using
    canonical Monte Carlo to simulate a system.  A simulation at a
    give temperature only provides information fo a small number of
    energy states.\label{fig:histograms}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-weights}
  \caption{The weight functions from different methods.}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-dos}
  \caption{A density of states plot demonstrating the difficulty of using
    canonical Monte Carlo to simulate a system.  A simulation at a
    give temperature only provides information fo a small number of
    energy states.\label{fig:dos}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-u}
  \caption{Specific internal energy.\label{fig:u}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-hc}
  \caption{Specific heat capacity.\label{fig:hc}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-rdf}
  \caption{Radial distribution function.\label{fig:rdf}}
\end{figure}
